---
title: "Activity 7 - Linear Discriminant Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r libraries, message=FALSE}
library(tidyverse)
library(tidymodels)
```

## Loading the Data
```{r dataload}
resume <- read.csv("https://www.openintro.org/data/csv/resume.csv")
```

## LDA
```{r LDA}
# Convert received_callback to a factor with more informative labels
resume <- resume %>% mutate(received_callback = factor(received_callback, labels = c("No", "Yes")))


# LDA
library(discrim)
lda_years <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS") %>% 
  fit(received_callback ~ log(years_experience), data = resume)

lda_years
```
The `group mean` for resumes that received a call back is higher than resumes that did not receive a call back.
The `group mean` is comparing the peaks of each density plot.

## Predictions

This outputs a long list of predictions so this must be consolidated into a confusion matrix.
```{r predictions}
predict(lda_years, new_data = resume, type = "prob")
```

The confusion matrix shows us that every record was classified as not getting a call back.
```{r confusion matrix}
augment(lda_years, new_data = resume) %>% 
  conf_mat(truth = received_callback, estimate = .pred_class)
```

The accuracy represents the probability of a record being a `no`.
```{r probabilities}
augment(lda_years, new_data = resume) %>% 
  accuracy(truth = received_callback, estimate = .pred_class)
```


## Challenge: Fit another model
Creating a linear model using the log() of `years_experience`.
```{r another model}
resume <- read.csv("https://www.openintro.org/data/csv/resume.csv")
lm_years <- lm(received_callback ~ log(years_experience), data = resume)
```

```{r predict}
aug_lm_years <- augment(lm_years)
```

```{r plot task 3}
resume %>% 
  ggplot(aes(x=received_callback, y=log(years_experience))) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point() + 
  theme_bw()
```

```{r chart residuals}
ggplot(data = aug_lm_years, aes(x = .fitted, y = .std.resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals") + 
  theme_bw()
```

```{r histogram}
ggplot(data = aug_lm_years, aes(x = .std.resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals") + 
  theme_bw()
```

